---
title: "2022 MAO ePrEP Project Data Plan"
author: "MAO DATA"
date: "02/06/2021"
output: 
  html_document:
    number_sections: yes
    toc: yes
    theme: cerulean
    toc_float: 
      collapsed: TRUE
      smooth_scroll: TRUE
      keep_md: FALSE  # knitr processes an r makdown input file , creates a markdown file then it is transforme to html by pandoc . The markdown file occupies space so delete it to make d size of ur html
---

# PART 2 : MONTHLY DATA



```{=html}
<style type="text/css">
h1 { /* Header 1 */
  font-size: 28px;
  color: Tomato;
}

  body{
  font-size: 13pt;
  font-family: "Calibri";
  color: Black;
}
</style>
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(leaflet)
library(rgdal)
library(tigris) 
library(tidyverse)
library(sf)
library(readxl)



library(Hmisc)    # **** describe(df)    # lists all categorical variables and summarize numeriical
library(pivottabler) #******VIP best for pivot table*** arguments:  qhpvt(df, rows, columns, calculations, ...) qhpvt(df, "app", "provider", "n()") # TOC = Train Operating Company  
library(readxl)
library(tidyverse)
library(aod)
library(ggplot2)
library(gridExtra)
library(VIM)
library(dplyr)
library(magrittr)
library(skimr)
library(naniar)

library(pivottabler)
library(rpivotTable)

library(visdat)
library(GGally)
library(janitor)
library(DT)
library(data.table)
library(ggmosaic)
library(writexl)
library(plotly)

library(formattable)

library(kableExtra)

library(webshot)

library(zoo)
```

<p>

 

</p>

<p>

 

</p>



<p>

 

</p>

-   Total number of unduplicated PrEP patients seen monthly. 





```{r eval=F}

 [1] "PatNamesort"             
 [2] "ptn"                     
 [3] "PatientChartNbr"         
 [4] "EncounterNbr"            
 [5] "ReasonClassDesc"         
 [6] "ReasonDesc"              
 [7] "EnctrOccurDate"          
 [8] "EnctrOccurTime(12hr)"    
 [9] "SvcCntrName"             
[10] "ProviderName"            
[11] "PatAssignedProvName"     
[12] "PatDateofLastVisit"      
[13] "PatLastVstDiagnosisCodes"
[14] "PatDateofFirstVisit"     
[15] "PatEthnicityDesc"        
[16] "PatHomeAddrCity"         
[17] "PatHomeAddrZip"          
[18] "PatHomeAddrSt"           
[19] "PatRaceDesc"             
[20] "PatDOB"                  
[21] "PatGenderDesc"           
[22] "PatRegistrationDate"     
[23] "EnctrStatusDesc"         
[24] "EnctrTypeDesc"           
[25] "PatLastInsBillDate"      
[26] "PatDeceasedDate"         
[27] "zipcode"                 
[28] "zip2"                    
[29] "TOTAL"                   
[30] "MONTH_"
```




```{r warning = FALSE, message=FALSE}
df<- read_excel("G:/EPREP 2022.xlsx", sheet = "monthDuplicatesRemoved")
#df<- read_excel("G:/E PREP DATABASE.xlsx", sheet = "2021q4")
df %<>% mutate(MONTH= zoo::as.yearmon(EnctrOccurDate))

#matrixplot(df)
#vis_dat(df,sort_type = F)
#tabyl(df,MONTH)

df2<-df %>%
  group_by(MONTH)%>% 
dplyr::summarise(Total_Monthly= n_distinct(ptn))%>% 
             mutate('Cumulative Total Patients Seen per Month' = cumsum(Total_Monthly))%>%
kable( booktabs = T,align = "c") %>%
kable_paper(full_width=F,position="left", "hover") %>%
 # row_spec(0, angle = -10) %>%
 # kable_classic(full_width = FALSE) %>%
column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "10em") %>% # , background = "yellow"
 column_spec(3, width = "10em", bold = T)

df2
#    library(mmtable2)
#    df%>%
#    mmtable(table_data = ptn)+
#    header_top(MONTH)+
#    header_left(PatRaceDesc)
#    table_format(locations = row_list,style= style_list)
#    colnames(df)
```



```{r}
# TESTING SPARKLINE
# mpg_list <- split(mtcars$mpg, mtcars$cyl)
# disp_list <- split(mtcars$disp, mtcars$cyl)
#inline_plot <- data.frame(cyl = c(4, 6, 8), mpg_box = "", mpg_hist = "",
#                          mpg_line1 = "", mpg_line2 = "",
#                          mpg_points1 = "", mpg_points2 = "", mpg_poly = "")
#inline_plot %>%
#  kbl(booktabs = TRUE) %>%
#  kable_paper(full_width = FALSE) %>%
#  column_spec(2, image = spec_boxplot(mpg_list)) %>%
#  column_spec(3, image = spec_hist(mpg_list)) %>%
#  column_spec(4, image = spec_plot(mpg_list, same_lim = TRUE)) %>%
#  column_spec(5, image = spec_plot(mpg_list, same_lim = FALSE)) %>%
 # column_spec(6, image = spec_plot(mpg_list, type = "p")) %>%
 # column_spec(7, image = spec_plot(mpg_list, disp_list, type = "p")) %>%
 # column_spec(8, image = spec_plot(mpg_list, polymin = 5))

```


```{r}
#coef_table <- data.frame(
##  Variables = c("var 1", "var 2", "var 3"),
#  Coefficients = c(1.6, 0.2, -8.0),
#  Conf.Lower = c(1.3, -0.4, -2.5),
#  Conf.Higher = c(1.9, 8.6, -1.4)
#) 

#data.frame(
#  Variable = coef_table$Variables,
#  Visualization = ""
#) %>%
#  kbl(booktabs = T) %>%
#  kable_classic(full_width = FALSE) %>%
 # column_spec(2, image = spec_pointrange(
 #   x = coef_table$Coefficients, 
 #   xmin = coef_table$Conf.Lower, 
 #   xmax = coef_table$Conf.Higher, 
 #   vline = 0)
 #   )

```


```{r}

#df5<-df %>%
#  group_by(MONTH) %>%
#  dplyr::add_count(count4dplyr, MONTH)%>%
#  ungroup()
#View(df5)

#df66<-df5%>%
#   distinct(ptn, .keep_all=TRUE)%>%
#  group_by(MONTH) %>%
#  select(n)

#df66
```

```{r}
#dim(df5)
# df6<-df %>%  
#   group_by(MONTH) %>%
#   dplyr::summarise(Total_Monthly= n_distinct(ptn))%>% 
#   mutate('Cumulative Unduplicated Total Patients Seen per Month' = cumsum(Total_Monthly))
# df6
  #dplyr::mutate(occ = dplyr::row_number())
#View(df5)
```


## Total number of unduplicated PrEP patients seen year to date is __184__ .   



```{r}
# remove
#df<- read_excel("G:/E PREP DATABASE.xlsx", sheet = "Sheet1")
#df<- read_excel("G:/E PREP DATABASE.xlsx", sheet = "zipcode #distance difference")
#tabyl(df,SvcCntrName,ReasonDesc)
#qhpvt(df, "ReasonDesc", "SvcCntrName", "n()")
#library(rpivotTable)
# rpivotTable(df1)
```



```{r eval=FALSE}
# colnames(dfvisit)
[1] "PatNamesort"             
 [2] "ptn"                     
 [3] "PatientChartNbr"         
 [4] "EncounterNbr"            
 [5] "ReasonClassDesc"         
 [6] "ReasonDesc"              
 [7] "EnctrOccurDate"          
 [8] "EnctrOccurTime(12hr)"    
 [9] "SvcCntrName"             
[10] "ProviderName"            
[11] "PatAssignedProvName"     
[12] "PatDateofLastVisit"      
[13] "PatLastVstDiagnosisCodes"
[14] "PatDateofFirstVisit"     
[15] "PatEthnicityDesc"        
[16] "PatHomeAddrCity"         
[17] "PatHomeAddrZip"          
[18] "PatHomeAddrSt"           
[19] "PatRaceDesc"             
[20] "PatDOB"                  
[21] "PatGenderDesc"           
[22] "PatRegistrationDate"     
[23] "EnctrStatusDesc"         
[24] "EnctrTypeDesc"           
[25] "PatLastInsBillDate"      
[26] "PatDeceasedDate"  



[27] "zipcode"                 
[28] "zip2"                    
[29] "TOTAL"                   
[30] "MONTH_"     

```


```{r warning = FALSE, message=FALSE}

#   df1 <- read_excel("G:/PREP ENCOUNTER ALL DEMOG.xlsx", sheet = "Sheet2")

 dfvisit<- read_excel("G:/EPREP 2022.xlsx", sheet = "Sheet1")

#dfvisit<- read_excel("G:/EPREP 2022.xlsx", sheet = "q2")
# dim(dfvisit)



#df<- read_excel("G:/E PREP DATABASE.xlsx", sheet = "2021q4")
#vis_dat(dfvisit,sort_type = F)
#View(df)
#df<-distinct(df, .keep_all=TRUE)
#tabyl(dfvisit,MONTH) 
dfvisit2<-dfvisit %>% arrange(ptn, desc(EnctrOccurDate))
df<-dfvisit2 %>%
  mutate(EnctrOccurDate= as.Date(EnctrOccurDate, format= "%d.%m.%Y")) %>%
  distinct(ptn, .keep_all = TRUE) # REMOVE DUPLICATES KEEP MOST RECENT



#df<-distinct(dfvisit, ptn, .keep_all = TRUE)
#dfs1<- df1[, c("ptn")] # SUBSET BY COLUMN NAME
# VIS_DAT STUFF
#vis_expect(df1, ~.x %in% dfmsm$ptn)
#vis_expect(df1, ~.x %in% dfdeactive$ptn)
#vis_guess(df1)
#vis_dat(df1)

#  dfs1<- df1[, c("ptn")] # SUBSET BY COLUMN NAME

df %<>% mutate(MONTH= zoo::as.yearmon(EnctrOccurDate))

#df %<>% mutate(yearmonth  = zoo::as.yearmon(EnctrOccurDate))

df<-df %<>% mutate(quarter  = zoo::as.yearqtr(EnctrOccurDate,format="%Y-%m-%d"))

df<-df %>%
  dplyr::mutate(YEAR = lubridate::year(EnctrOccurDate), 
                month = lubridate::month(EnctrOccurDate),
                week = lubridate::week(EnctrOccurDate),
                yday = lubridate::yday(EnctrOccurDate),  ####
               quarter2 = lubridate::quarter(EnctrOccurDate),
                day = lubridate::day(EnctrOccurDate))

df=df%>%mutate_at("quarter", as.character)

#dim(df)

#dfmsm <- read_excel("G:/msm feb 2022.xlsx",sheet = "Sheet1")
dfmsm <- read_excel("G:/msm july 2022.xlsx",sheet = "Sheet1")
#  dim(dfmsm)
#  colnames(dfmsm)
dfmsm<-dfmsm%>%dplyr::select(ptn,msm)


#dim(dfmsm)
dfINS<- read_excel("G:/EPREP 2022.xlsx", sheet = "INS")
dfINS<-dfINS%>%dplyr::select(ptn,INSURANCE)

#vis_dat(df,sort_type = F)
#vis_dat(dfmsm,sort_type = F)
#vis_dat(dfINS,sort_type = F)

df<-list(df,
         dfmsm,
         dfINS) %>% reduce(left_join, by = "ptn")

#dim(df)

#dfseenMonthly<-qhpvt(df, "YEAR", "MONTH", "n()")
#dfseenMonthly
#dfinacTable<-qhpvt(df, "YEAR", "inactive", "n()")
#View(df)

#  dim(df)


df<-df %>% arrange(ptn, desc(EnctrOccurDate))


df<-df %>%
  mutate(EnctrOccurDate= as.Date(EnctrOccurDate, format= "%d.%m.%Y")) %>%
  distinct(ptn, .keep_all = TRUE) # REMOVE DUPLICATES KEEP MOST RECENT

#  dim(df)

# rpivotTable(df)


```



```{r}

#-   A crosstabulation of PrEP patients by date of last encounter and EMR status ( active or inactive)
#tabyl(df,deactivated,ActiveS)%>%adorn_totals('row') %>%adorn_pct_formatting()

#tabyl(df,MSMS,msm)

#tabyl(df,MSMS)%>%adorn_totals('row') %>%adorn_pct_formatting()

#tabyl(df,TRANSGENDERS)%>%adorn_totals('row') %>%adorn_pct_formatting()
#tabyl(df,INSUREDS,PatCv1PlanName)

#qhpvt(df,"PatCv1PlanName", "INSUREDS",  "n()")

#tabyl(df,quarter)
```

```{r warning = FALSE}

#dim(df)

df %<>%            #  ds converts dob to date from posixt
  mutate(PatientAge1= as.Date(PatDOB, format= "%d.%m.%Y"))     #  ds converts dob to date

df$PatientAge1 = as.numeric(difftime(Sys.Date(),df$PatientAge1, units = "weeks"))/52.25

df$PatientAge1 <- round(df$PatientAge1)


#### RACE RECODE
df$PatRaceDesc <- gsub("'", '', df$PatRaceDesc)

df <- df %>%   
     mutate_at(c("PatRaceDesc"),
               funs(recode(., `American Indian or Alaska Native`='OTHER',
                             `Asian`='ASIAN',
                           `Black or African American`='AFRICAN AMERICAN',
                           `Latino/Hispanic`='HISPANIC',
                           `Native Hawaiian`='OTHER',
                           `Other Pacific Islander`='OTHER',
                           `Race Not Reported - Dont Know`='OTHER',
                           `Race Not Reported - Not Ascertained`='OTHER',
                           `Race Not Reported - Refusal`='OTHER',
                          `White`='WHITE',
                           	 .default ='CHECKmISSING')))



#quarteryr<-as.charater(quarteryr)

#toString(df$quarteryr)
#df %>% mutate(employed=recode(employed, "FALSE"="prov"))

#quarteryr <- data.frame(lapply(quarteryr, as.character))

attach(df)
df$AGE[PatientAge1 >= 65] <- "65+"
df$AGE[PatientAge1 > 44 & PatientAge1 <= 64] <- "45-64"
df$AGE[PatientAge1 > 24 & PatientAge1 <= 44] <- "25-44"
df$AGE[PatientAge1 <= 24] <- "18-24"
detach(df)


#dfinacTable<-tabyl(df, YEAR, inactive)
#dfinacTable
#dfinacTable<-tabyl(df, YEAR, inactive)
#dfinacTable
#qhpvt(df, "AGE", "PatGenderDesc", "n()")
#tabyl(df,quarter)

#vis_guess(df)
#vis_dat(df,sort_type = F)
#View(df)

#vis_dat(df,sort_type = F)

#   rpivotTable(df)

```




```{r}
#dfinacTable<-qhpvt(df, "YEAR", "inactive", "n()")
#dfinacTable1<-as.data.frame(dfinacTable)
#df$inactive[is.na(df$inactive)]<-"ACTIVE"
#dfinacTable1<-as.data.frame(dfinacTable)
#dfinacTable
#dfinacTable<-qhpvt(df, "YEAR", "inactive", "n()")
#tabyl(df, YEAR, inactive)
#dfinacTable<-tabyl(df, YEAR, inactive)
#dfinacTable1<-as.data.frame(dfinacTable)
#dfinacTable1
#d[is.na(d)]<-0
#dfinacTable3<-dfinacTable1 %>%  rename("YEAR" ="YEAR",
 #                                      "INACTIVE"="INACTIVE",
#  

#library(rpivotTable)
#rpivotTable(df)

```

<p>

 

</p>

\newpage

## PREP PATIENT BY DATE OF LAST ENCOUNTER

<p>



 
 
 

</p>

```{r  warning = FALSE, message=FALSE}
library(crosstalk)
library(reactable)

EnctrOccurDate<-as.POSIXct
quarter<-as.POSIXct

#df<-df[1:20, c("ProviderName", "SvcCntrName", "ReasonDesc", "ptn","EnctrOccurDate","week)]

df2<-df[ c("TOTAL", "ptn", "ReasonDesc","EnctrOccurDate","ProviderName","month","quarter")]
data <-SharedData$new(df2)

bscols(
  widths = c(3, 9),
  list(filter_slider("month", "MONTH OF LAST APPOINTMENT", data, ~month),
    filter_select("mfr", "PROVIDER", data, ~ProviderName),
    filter_select("qtr", "QUARTER", data, ~quarter),
   # filter_checkbox("type", "APPOINTMENT TYPE", data, ~ReasonDesc),
    filter_select("type", "APPOINTMENT TYPE", data, ~ReasonDesc)
   # filter_slider("price", "ptn", data, ~ptn, width = "100%")
   # filter_slider("EnctrOccurDate", "EnctrOccurDate", data, ~EnctrOccurDate)
   # filter_slider("week", "week", data, ~EnctrOccurDate
        ),
# plot_ly(data, x = ~EnctrOccurDate, color = ~ReasonDesc) %>% config(displaylogo = FALSE)%>%add_histogram(),
 plot_ly(data,type="scatter",y = ~ptn, x = ~EnctrOccurDate,color= ~ReasonDesc,alpha = 0.5),#,size= ~YEAR
  reactable(data,
            groupBy = "month",
             columns=list(TOTAL=colDef(aggregate="count"),
                          month=colDef(minWidth = 140)),
            minRows = 5,
            bordered=T,
             striped=T,
            pagination = F,
            outlined=T,
           highlight=T,
          compact=F,
          resizable=T,
           theme=getOption("reactable.theme")),
  reactable(data,
            groupBy = "ReasonDesc",
             columns=list(TOTAL=colDef(aggregate="count"),
                         #TOTAL = colDef(footer = function(values) sprintf(sum(values))),  # not workin       
                        # ProviderName=colDef(minWidth = 2),
                        # ReasonDesc=colDef(footer="Total"),
                          ReasonDesc=colDef(minWidth = 300)),
            minRows = 8,
            bordered=T,
             striped=T,
            pagination = F,
            outlined=T,
           highlight=T,
          compact=F,
          resizable=T,
           theme=getOption("reactable.theme"))

  )

```

<p>

 

</p>

<p>

 

</p>

\newpage


# VISITS BY APPOINTMENT TYPE



<p>&nbsp;</p>


```{r}
# VISITS

#qhpvt(dfvisit, "month", "ReasonDesc", "n()")


#tabyl(dfvisit,ReasonDesc)%>%
#  adorn_totals('row')%>%
#  adorn_pct_formatting()%>%
# kable( booktabs = T) %>%
# kable_paper(full_width=F,position="left", "hover")


```



```{r}
#colnames(dfv)
```


```{r}
#colnames(dfv)

#tabyl(dfv,SvcCntrName)
```






```{r warning = FALSE, message=FALSE}
library(lubridate)
library(dplyr)
library(zoo)
#dfv <- read_excel("G:/PREP ENCOUNTER ALL DEMOG.xlsx", sheet = "Sheet1")
#dfv <- read_excel("G:/PREP ENCOUNTER ALL DEMOG.xlsx", sheet = "prepvisit")

dfv<- read_excel("G:/EPREP 2022.xlsx", sheet = "Sheet1")
#vis_dat(dfvisit,sort_type = F)
#View(df)
EnctrOccurDate<-as.POSIXct

dfv %<>% mutate(MONTH  = zoo::as.yearmon(EnctrOccurDate))
dfv %<>% mutate(yearmonth3= as.Date(MONTH, format= "%b%y"))    #  ds converts yearmonth to date from posixt

#plot(dfv2)
#dfv3<-dfv2[-3] # drop column 3
#vis_dat(dfv2)

dfv<-dfv %<>% mutate(quarter  = zoo::as.yearqtr(EnctrOccurDate,format="%Y-%m-%d"))

dfv<-dfv %>%
  dplyr::mutate(YEAR = lubridate::year(EnctrOccurDate), 
                month = lubridate::month(EnctrOccurDate),
                week = lubridate::week(EnctrOccurDate),
                yday = lubridate::yday(EnctrOccurDate),  ####
               quarter2 = lubridate::quarter(EnctrOccurDate),
                day = lubridate::day(EnctrOccurDate))

# View(dfv)

#  colnames(dfv)

#esquisse::esquisser(dfv)
#tabyl(dfv,month)
```


```{r}


```


```{r}

# df<- subset(dfv, month <= 9)
# tabyl(df,SvcCntrName,month)

# df%>% 
#   tabyl(SvcCntrName,month) %>%
#   adorn_totals(where="row") %>%
#   adorn_totals(where="col") %>%
 # adorn_percentages("col") %>%
#  adorn_pct_formatting(digits=2) %>%
#  adorn_ns(position = "front") %>%
#   kable( booktabs = T) %>%
 #kable_styling(bootstrap_options = c("striped", "hover"))
# kable_paper(full_width=F,position="left", "hover")
```
```{r}


#  c<-df%>% tabyl(ReasonDesc,SvcCntrName)
#  write_xlsx(c, "G:/rsn by cln.xlsx")  # OUT PUT TO CHECK
```



```{r warning = FALSE, message=FALSE}
library(pivottabler)

#dim(dfv)

#dfv<-dfv%>%filter(quarter2%in% c(4))
#dfv<-dfv%>%filter(quarter%in% c('2020 Q4'))

#tabyl(dfv,ReasonDesc,AppoitmentType)%>%adorn_totals('row')
#dim(dfv)

#qhpvt(dfv,"ReasonDesc", "MONTH",  "n()")




pt <- PivotTable$new()
pt$styles$addStyle(styleName="NewHeadingStyle1", list(
      "font-family"="Arial",
      "font-size"="0.75em",
      padding="2px",
      border="1px solid lightgray",
      "vertical-align"="middle",
      "text-align"="center",
      "font-weight"="bold",
      #"background-color"="Gold",
      "xl-wrap-text"="wrap"
    ))
pt$styles$addStyle(styleName="CellStyle1", list(
      "font-family"="Arial",
      "font-size"="0.75em",
      padding="2px 2px 2px 8px",
      border="1px solid lightgray",
      "vertical-align"="middle",
      #"background-color"="Yellow",
      "text-align"="center"
    ))
pt$addData(dfv)
pt$addColumnDataGroups("MONTH")      # row 1
#pt$addColumnDataGroups("msm",addTotal=F)   # row2
pt$addRowDataGroups("ReasonDesc") # ,totalCaption="Grand Total"  column 1
pt$defineCalculation(calculationName="TotalTrains",
                     summariseExpression="n()",
                     cellBaseStyleName="CellStyle1",
                     headingBaseStyleName="NewHeadingStyle1") #,format="%.1f"
pt$evaluatePivot()
pt$renderPivot(styleNamePrefix="orzy007")

#tabyl(dfv,AppoitmentType)%>%adorn_totals('row') %>%adorn_pct_formatting()

# define the font and colours
```

```{r warning = FALSE, message=FALSE}
ggr<- dfv %>%
  group_by(month,ReasonDesc) %>%
  dplyr::summarise(count=n(),.groups="drop")

# esquisse::esquisser(ggr)

#  USING GGPLOT TO PLOT LINE CHART
 # PL<-(ggplot(ggr) +
#   aes(x = month, y = count, colour = ReasonDesc) +
#   geom_line(size = 0.5) +
#   scale_color_hue(direction = 1) +
#   labs( x = "MONTH",
 #    title = "PrEP APPOINTMENT TYPE TREND")+
    #color = "ORANGE") +
 #  theme_minimal() +
 #  theme(plot.title = element_text(face = "bold", hjust = 0.5)))
  # ggplotly(PL)

ggr%>%
  plot_ly(x=~month,
          y=~count,
          group_by=~ReasonDesc,
       #  type="scatter",
         color=~ReasonDesc, 
         mode="lines+markers")%>%
layout(title="PrEP APPOINTMENT TYPE TREND")%>%
  config(displayModeBar=F)

```




\newpage


# DEMOGRAPHICS

<p>

 
 
 
 

## AGE BY GENDER

<p>

 

 
 

```{r}
qhpvt(df, "AGE", "PatGenderDesc", "n()")
```



```{r}

```

<p>

 

</p>


```{r}
# colnames(df)
```

```{r warning = FALSE}

df%>% 
  tabyl(AGE,PatGenderDesc) %>%
  adorn_totals(where="row") %>%
  adorn_totals(where="col") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits=2) %>%
  adorn_ns(position = "front") %>%
  kable( booktabs = T) %>%
 #kable_styling(bootstrap_options = c("striped", "hover"))
kable_paper(full_width=F,position="left", "hover")
```

```{r warning = FALSE}
library(ggplot2)
p1<-(ggplot(df, aes(x=as.factor(PatGenderDesc), fill=as.factor(AGE)))+
  geom_bar(aes( y=..count../tapply(..count.., ..x.. ,sum)[..x..]), position="dodge" ) +
  geom_text(aes( y=..count../tapply(..count.., ..x.. ,sum)[..x..], label=scales::percent(..count../tapply(..count.., ..x.. ,sum)[..x..]) ),
            stat="count", position=position_dodge(0.9), vjust=-0.5)+
  ylab('Percent of Age Group %') +
    xlab('GENDER') +
    theme(axis.text.x = element_text(angle = 45))+
  scale_y_continuous(labels = scales::percent))

p1

#ggplotly(p1,height=400,width=600)

```


\newpage


## AGE BY RACE

<p>

 

</p>

```{r warning = FALSE}

df%>% 
  tabyl(AGE,PatRaceDesc) %>%
  adorn_totals(where="row") %>%
  adorn_totals(where="col") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits=2) %>%
  adorn_ns(position = "front") %>%
  kable( booktabs = T) %>%
 #kable_styling(bootstrap_options = c("striped", "hover"))
kable_paper(full_width=F,position="left", "hover")
```

```{r}
library(ggplot2)
p1<-(ggplot(df, aes(x=as.factor(PatRaceDesc), fill=as.factor(AGE)))+
  geom_bar(aes( y=..count../tapply(..count.., ..x.. ,sum)[..x..]), position="dodge" ) +
  geom_text(aes( y=..count../tapply(..count.., ..x.. ,sum)[..x..], label=scales::percent(..count../tapply(..count.., ..x.. ,sum)[..x..]) ),
            stat="count", position=position_dodge(0.9), vjust=-0.5)+
  ylab('Percent of Age Group, %') +
    xlab('RACE') +
    theme(axis.text.x = element_text(angle = 45))+
  scale_y_continuous(labels = scales::percent))

ggplotly(p1,height=400,width=750)



```



<p>

 

</p>


\newpage

## INSURANCE

</p>





```{r warning = FALSE}


tabyl(df,INSURANCE)%>%
  adorn_totals('row')%>%
  adorn_pct_formatting()%>%
 kable( booktabs = T,align = "c") %>%
 kable_paper(full_width=F,position="left", "hover")

```
</p>
## RISK

</p>

```{r warning = FALSE}

df<-df %>% replace_na(list(msm = "HETEROSEXUAL")) #replace na in missing merged msm column with heterosexual


df%>% 
  tabyl(msm,PatGenderDesc) %>%
  adorn_totals(where="row") %>%
  adorn_totals(where="col") %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits=2) %>%
  adorn_ns(position = "front") %>%
  kable( booktabs = T) %>%
 #kable_styling(bootstrap_options = c("striped", "hover"))
kable_paper(full_width=F,position="left", "hover")

```

<p>

 

</p>



<p>

 

</p>


\newpage


# NUMBER OF PATIENTS BY COUNTY

<p>

 

</p>

<p>

 

</p>


```{r}
# df<- read_excel("G:/aug to jan dill.xlsx", sheet = "new hiv prep aut to jan")


```


<p>

 

</p>

```{r}
#colnames(df)
#colnames(dfm)
#colnames(dfz)
#vis_dat(dfz,sort_type = F)
#vis_dat(df,sort_type = F)
```

```{r warning = FALSE, message=FALSE}

dfz<- read_excel("G:/ZIP_CODE_DATABASE22.xlsx",sheet = "Sheet1")


#df <- read_excel("G:/msm between 13 - 34 MOST RECENT ENCOUNTER BY R_.xlsx",sheet = "13 to 34")
#dim(df)
#View(df)
#colnames(dfz)


#df <- sapply(df[, c(18)], as.numeric)

#df<-df %>%  rename("zipcode"="PatHomeAddrZip") # rename  PatHomeAddrZip to zipcode so dt df can be merged with my county zipcode data base

dfm= df %>% left_join(dfz,by="zipcode")
# describe(dfz)
# tabyl(dfz,county,state)
#vis_dat(dfm,sort_type = FALSE)


# GROUP AND COUNT COUNTY that you just merged
dfcountygp<-dfm %>%
  group_by(county) %>%
  dplyr::summarise(density=n())

dfcountygp1<-dfm %>%
  group_by(county) %>%
  dplyr::summarise(density=n())


dfcountygp<-dfcountygp %>%  dplyr::rename("NAME"="county")

# rpivotTable(dfm)
```

```{r include = FALSE}
library(sf)
st_drivers()
#knitr::opts_chunk$set(echo = FALSE)
# read alabama county shae file into dfc 
dfc <- counties("01")
st_drivers()



#colnames(df)
```

```{r warning = FALSE, message=FALSE}
#dfa <- read_excel("G:/alabama merge to get chloropleth leaflet.xlsx",sheet ="Sheet5")



dfm= dfc %>% left_join(dfcountygp,by="NAME")



#df$INTPTLON2 = as.numeric(gsub("\\-", "", df$INTPTLON))

# get removed from simple note

```








</p>

```{r  warning = FALSE, message=FALSE}

library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)
library(maptools)
library(ggthemes)

usa <- map_data("county")  # get basic map data for all USA counties 

al = subset(usa, region == "alabama")  # subset to counties in AL 


library(stringr)
al$county = str_to_title(al$subregion)  # Create a new variable called county with the correct format

library(sp) 
getLabelPoint <- # Returns a county-named list of label points
function(county){Polygon(county[c('long', 'lat')])@labpt}
centroids = by(al, al$county, getLabelPoint)     # Returns list
centroids2 <- do.call("rbind.data.frame", centroids)  # Convert to Data Frame
centroids2$county = rownames(centroids)
names(centroids2) <- c('clong', 'clat', "county")
```




```{r  warning = FALSE}

dfm2= al %>% left_join(dfcountygp1,by="county")

ff<-(ggplot() + 
  geom_polygon(data = dfm2, aes(x = long, y = lat, 
   group = group,
    fill = density), color = "black") + 
 coord_fixed(1.3) +
  geom_text(data = centroids2, aes(x = clong, y = clat, label = county), 
            color = "black", size = 2.25) + 
  scale_fill_distiller(palette = "YlOrRd",direction=-1,trans="reverse") + # palette eg GrandBudapest1 ,Spectral,Darjeeling1
  labs(fill = "Number of PrEP Clients") + 
  theme_map() + theme(legend.position = "bottom"))
  
  
# ds prints out leaflet map 
 pp12 <-ggplotly(ff, tooltip= "density",height=900,width=900)
 pp12

#head(dfm2)

```

<p>







\newpage





## NUMBER OF PATIENTS BY COUNTY

```{r}

#    dfm= df %>% left_join(dfz,by="zipcode")
#colnames(dfm)

#   countyTable<-tabyl(dfm,county)%>%
#    arrange(desc(n))%>%
 #    adorn_totals('row')%>%
 #    adorn_pct_formatting()%>%
#    kable( booktabs = T) %>%
#    kable_styling(full_width=F,position="left",bootstrap_options = c("striped", "hover"))
#   countyTable

```


```{r}

dfm= df %>% left_join(dfz,by="zipcode")
#colnames(dfm)

countyTable<-tabyl(dfm,county)%>%
  arrange(desc(n))%>%
  adorn_totals('row')%>%
  adorn_pct_formatting()%>%
 kable( booktabs = T) %>%
 kable_styling(full_width=F,position="left",bootstrap_options = c("striped", "hover"))%>%
  scroll_box(width = "235px",height="430px")
countyTable

```






```{r}
#\newpage
```







```{r warning = FALSE, message=FALSE}

#   datatable(dfcountygp1,
#             rownames=F,
#             options=list(order=list(1,"desc"))) %>% # order list =sort col 1 desc
 # options=list()%>% 
#     formatStyle('density', 
#                 fontWeight = styleInterval(5, c('normal', 'bold')
       #                    )
#                 ) %>%
#    formatStyle( 'density',
#                 background = styleColorBar(dfcountygp1$density,'steelblue'),
#                 backgroundSize = '100% 90%',
#                 backgroundRepeat = 'no-repeat',
 #                backgroundPosition = 'center')
 
  
```




```{r warning = FALSE, message=FALSE}

 
  
```




<p>

 

</p>








\newpage








 
